---
title: "STAT 450 HTML Intro Assignment"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


## Introduction 
About Harry Xu: Harry is a 4th year Stats Major and Commerce Minor Student at UBC. He likes sports a lot and he goes to the gym often. He recently got into snowboarding and longboarding. He is taking Stat 450 this year and he is very excited to work on a case for a client. Today in the seminar, Jan 11th 2018, Harry did some knitting and he thinks it's pretty cool. His friends also helped him knit with different tools.

## Favourite Equation: 
My favourite equation is: $1^2+2^2+3^2 +.... + n^2 = \frac{(n+1)(n+2)(2n+1)}{6}$ This equation is one of the fundemental equations used in Calculus.

## Favourite Dataset:

My favourite Dataset: is the S&P500 dataset dated back since Jan of 1871, which I downloaded online. Here is the first 5 rows of the dataset. 

``` {r, echo = FALSE}

SP500 <- read.csv("data_csv.csv")
head(SP500, n =5)
``` 
### 
##
# 
####Here is the graph showing the S&P500 Real Price vs. Time:

``` {r, echo = FALSE}
# library(tseries)
# library(zoo)
# timeseries <- ts(data = SP500$Real.Price)
# plot(timeseries)
plot(SP500$Date, SP500$Real.Price, xlab = "Time", ylab = "Real Price", main = "S&P500")
```


